% Template creds: Xavier Danaux 

\documentclass[10pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
% \usepackage[scale=0.8]{geometry}
 \usepackage[left=2cm, right=2cm, top=1.7cm, ,bottom=1.7cm]{geometry}
\usepackage{multicol}


\usepackage{import}

% personal data
%1016 Washington Ave SE
%Minneapolis, MN  55414
%United States
\name{Alhaitham}{Al Jabri}
%   \title{Software Developer}                               % optional, remove / comment the line if not wanted
 
\address{Muscat}{Oman}% optional, remove / 

\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right 
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

  
  
\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-20mm}

\begin{center}
\begin{tabular}{ c c c c c }  \faEnvelopeO\enspace jabri.dev@gmail.com &  \faGlobe\enspace \href{jabri.dev}{jabri.dev} & \faGithub\enspace \href{https://github.com/aljab012}{aljab012}   & \faLinkedin \enspace \href{https://www.linkedin.com/in/alhaitham/}{/in/alhaitham}  & \faMobile\enspace +968 91929531
\end{tabular}
\end{center}
% \vspace{2mm}

% start education sec
\section{EDUCATION}
{\customcventry{Dec 2020 }{B.S. in Computer Science, GPA: 3.56/4.00 }{University of Minnesota-Twin Cities}{Minneapolis, MN}{}{\vspace{2mm} \textbf{Relevent Coursework:} Advanced Algorithms and Data Structures (Grad). Animation and Planning in Games (Grad). Introduction to Artificial Intelligence. Internet Programming. Practice of Database Systems. Programming Graphics and Games. Program Design and Development.}}

% \vspace{1mm}
% end education sec



% start experience
\section{EXPERIENCE}


{\customcventry{Sept 2021 - Present}{Software Engineer - Full-time}{Rihal - Data Solutions}{Muscat, Oman}{}
{\begin{itemize}
  \item Deployed apps to production servers using {\textbf {Docker}}.
  \item Worked as the {\textbf {Team Leader}} to handle requirement gathering with stakeholders.
  \item Reviewed over 50+ pull requests on {\textbf {GitHub}} to improve code quality and practices.
  \item Constructed {\textbf {CI/CD infrastructure}} using {\textbf {GitHub Actions}} and {\textbf {Harbor}} as a private registry.
  \item Updated over 30+ deprecated end-to-end tests using {\textbf {Cypress}}.
  \item Added 10+ core features independently to an existing project using {\textbf {Golang}} for back-end and {\textbf {React}} with Typescript for front-end.
\end{itemize}
}
}
{\customcventry{Apr 2021 - Sept 2021}{Software Engineer - Intern}{Rihal - Data Solutions}{Muscat, Oman}{}
{\begin{itemize}
  \item Accelerated {\textbf {PostgreSQL}} queries with cached materialized views resulting in {\textbf {1000x speed}} improvement.
  \item Updated the existing front-end interface from {\textbf {Material-UI}} to {\textbf {Carbon Design System}}.
  \item Designed and built a new dashboard to show live metrics from database.
\end{itemize}
}


% {\customcventry{Sept 2016 - Aug 2017}{Student Security Monitor}{Department of Public Safety, University of Minnesota-Twin Cities}{Minneapolis, MN}{}
% {\begin{itemize}
%   \item Monitored buildings and checked for all doors and windows to ensure safety.
%   \item Investigated any matter of rule violation and complaints.
%   \item Detected suspicious activities and watched for criminal acts and rule infractions.
% \end{itemize}
% }
% end experience

% start project sec
\section{PROJECTS}{
% TODO: ADD links
{
{\customcvproject{\textbf{Boids and Flocking Simulation - Coursework:} }{Jul 2020 }
{\begin{itemize}
  \item Created multi-agent flocking simulation using processing framework.
  \item Simulated systems of multiple interacting particles in 2D.
  \item Allowed the user to interact with the simulation using the keyboard for a better user experience.
\end{itemize}
}
}
% \vspace{1mm}


{\customcvproject{\textbf{Single Agent Navigation AI Simulation - Coursework:}}{Jul 2020}
{\begin{itemize}
  \item Developed an app using Processing framework that simulates single-agent navigation system. 
  \item Built a 3D graphic window that displays a moving boat navigating between obstacles. 
  \item Allowed the user to specify the starting and the ending positions of the agent or assigned it randomly by the program.
\end{itemize}
}


% \vspace{1mm}
    \customcvproject{\textbf{Buy and Sell Web Application - Coursework:}}{Sept 2019}
{\begin{itemize}
  \item Built an interactive Flask web application that allowed students to sign up and log in to the website.
  \item Developed the app to allow students to sell and buy books and publish events on the website.
  \item Incorporated the use of multiple frameworks and libraries such as SqlAlchemy, WTForms, and Bootstrap.
\end{itemize}
}



}
}
}
% end project sec

% start skills sec
\section{SKILLS}
{\customcvproject{Languages \& Frameworks:}{}
{\begin{itemize}
  \item Fluent: Golang, PostgreSQL, Typescript/JavaScript, React, HTML, SASS/CSS.
  \item Familiar: OCaml, Java, C/C++, Python, Django/Flask, x86 assembly.
\end{itemize}
}
{\customcvproject{Miscellaneous:}{}
{\begin{itemize}
  \item Bash, Docker, Cypress, Webpack, OPA, Git/GitHub, Linux and Emacs.
\end{itemize}
}
}
}

% end skills sec


% start leadership sec
\section{LEADERSHIP}
\begin{minipage}{\maincolumnwidth}%
    	\begin{itemize}
          \item \customcvproject{Omani Students Union, Treasurer}{Sept 2019 - Jan 2020}{}
        \item \customcvproject{Association for Computing Machinery, Member}{Jan 2017 - Sept 2019}{}
		\end{itemize}
\end{minipage}%
% end leadership sec


% start of award sec
\section{AWARDS}
\begin{minipage}{\maincolumnwidth}%
    	\begin{itemize}
          \item \customcvproject{College of Science and Engineering, Dean’s List}{ Fall 2019 and Spring 2019}{}
          \item \customcvproject{Ministry of Higher Education - Oman, Full-ride merit scholarship to attend college}{Sept 2015}{}
		\end{itemize}
\end{minipage}%
}
% end of awards sec

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a 
\end{document}